Open source symbolic multibody dynamics software

### 2012-03-05 PetersonGedeHubbard2012.tex
Wrote wrap up sentence for section 2
Finished abstract.

\begin{abstract}
  Abstract here.
\keywords{symbolic dynamics software, control, nonholonomic systems,
          constrained systems}
\end{abstract}

@@

% Not sure which bibliography style we are supposed to use
%\bibliographystyle{spphys}       % APS-like style for physics
%\bibliographystyle{spbasic}      % basic style, author-year citations
\bibliography{library}   % name your BibTeX data base
\bibliographystyle{spmpsci}      % mathematics and physical sciences
\end{document}

>>>>

\begin{abstract}
  We present a systematic procedure for linearizing equations of motion
  governing constrained multibody systems which have been derived with Kane's
  method.  The procedure avoids differential algebraic equations and yields
  linear relationships between time derivatives of generalized
  coordinates/speeds (both independent and dependent) and independent
  generalized coordinates/speeds and exogenous inputs.  These minimal
  linearized equations effectively embed the constraints within them, and
  enable stability analysis and control system design without the need to
  explicitly address the constraints.  We numerically validate the results on a
  well studied model of a bicycle which includes both configuration and
  velocity constraints.
\keywords{symbolic dynamics, control, constrained multibody systems}
\end{abstract}

@@

% Not sure which bibliography style we are supposed to use
%\bibliographystyle{spphys}       % APS-like style for physics
%\bibliographystyle{spbasic}      % basic style, author-year citations
\section{Conclusion}

\bibliography{library}   % name your BibTeX data base
\bibliographystyle{spmpsci}      % mathematics and physical sciences
\end{document}
